---
title: "Simulation Results"
output: pdf_document
classoption: landscape
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(tibble)
library(magrittr)
library(coda)
setwd("~/Desktop/Chakravarti_Lab/git")
#load_all("CNPBayes_trios")
load_all("triostats")

library(knitr)
library(kableExtra)
library(ggplot2)
library(reshape2)
library(plyr)
library(dplyr)
library(tidyverse)
library(gtools)
library(splitstackshape)
library(stringr)
```

## Simulation Overview

Used 12 sets of parameters for simulation (shown in the table below) for a deletion region with CN 0, 1 , 2 and thetas (mean intensity) fixed at -3, 0.15, 1.2 respectively. Variance fixed at 0.2. The mixture proportions were varied between p=0.1 - 0.5 and the number of trios (N) fixed at 50, 100, 250 and 1000 for each set of variance parameters. These 12 parameters were replicated 1000x - a total of 2400 simulations were run.

For these simulations, we also calculate a delta parameter that represents the Euclidean distance of the estimated simulation parameters from the fixed simulation parameters. 


```{r params, echo=FALSE}
params.table <- matrix(c(1:12), nrow=3, ncol=4, byrow=T,
                       dimnames = list(c("p=0.5", "p=0.3", "p=0.1"),c("N=50", "N=100", "N=250", "N=1000")))
params.table
```

\newpage
### Model comparison at for different mixture proportions for the same N

#### N = 50

```{r read, echo=F, warning=F}
setwd("~/Desktop/Chakravarti_Lab/Submissions/nov27.results/results.origseed2")

file.no <- seq(1,2400, by=1)
L <- length(file.no)
results.list <- vector("list",L)
results.list2 <- vector("list",L)

for (i in 1:L){
  ia <- file.no[i]
  file.names <- paste0("params_",ia,".rds")
  params.in <- readRDS(file.names)
  data.read <-  simdata.read(params.in)
  stables <- summarise_results(data.read)
  #simresults <- overall_results(stables)
  #results.list[[i]] <- simresults
  simresults2 <- overall_results2(stables)
  results.list[[i]] <- simresults2

}

#rtable <- output_results(results.list)
rtable <- output_results2(results.list)
rtable.expand <- rtable_plotprep(results.list, reps=200)

leng <- length(results.list)
# for p=0.5
file.no1 <- seq(1,leng, by=12)

# for p=0.3
file.no2 <- seq(5,leng, by=12)

# for p=0.1
file.no3 <- seq(9,leng, by=12)
file.no <- sort(c(file.no1, file.no2, file.no3))

results.list1 <- results.list[file.no]
results.list1a <- results.list[file.no1]
results.list1b <- results.list[file.no2]
results.list1c <- results.list[file.no3]

rtable1 <- output_results2(results.list1)
rtable1a <- output_results2(results.list1a)
rtable1b <- output_results2(results.list1b)
rtable1c <- output_results2(results.list1c)

```

#####What is the overall accuracy for N=50?

```{r data1a, echo=F}

rtable.overall <- rtable_overall(rtable1)
#rtable.osmaller <- rtable_overalls(rtable1)
kable(rtable.overall) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```

#####What is the overall accuracy for N=50 by allele frequency?

```{r data1b, echo=F}

#rtable.af <- rtable_af(rtable1a, rtable1b, rtable1c)
rtable.afs <- rtable_afs(rtable1a, rtable1b, rtable1c)
kable(rtable.afs) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```
  
  
\newpage
#####What is the accuracy for N=50 by allele frequency stratified by whether parents were genotyped correctly?


```{r data1c, echo=F}

#rtable.pc <- rtable_pc(rtable1a, rtable1b, rtable1c)
rtable.pcs <- rtable_pcs(rtable1a, rtable1b, rtable1c)
kable(rtable.pcs, caption = "Parents Correct") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

#rtable.pic <- rtable_pic(rtable1a, rtable1b, rtable1c)
rtable.pics <- rtable_pics(rtable1a, rtable1b, rtable1c)
kable(rtable.pics, caption = "Parents Incorrect") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```
  
  
\newpage
#####What is the accuracy for N=50 by specific parental genotype?


```{r data1d, echo=F}

rtable.geno1 <- rtable_geno(rtable1a)
rtable.geno2 <- rtable_geno(rtable1b)
rtable.geno3 <- rtable_geno(rtable1c)

kable(rtable.geno1, caption = "p=0.5") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
kable(rtable.geno2, caption = "p=0.3") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
kable(rtable.geno3, caption = "p=0.1") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```

\newpage  
#####Comparison of Overall Child Accuracy?


```{r comparison 1, echo=FALSE, warning=FALSE}

rtable.accur <- rtable.expand %>% 
  filter(geno=="all") %>%
  filter(size.labels=="N50")
ggplot(rtable.accur, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=af.labels)) + geom_abline(intercept=0) + xlim(0.5,1) + ylim(0.5,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Overall Child Accuracy")
```
  
  
\newpage
#####What does the data look like across the replicates (boxplot)?

```{r plots 1a, echo=FALSE, warning=FALSE, fig.align='center'}
rtable.box <- rtable.expand %>%
  filter(geno=="cn2" | geno=="cn1" | geno=="cn0") %>%
  filter(size.labels=="N50")
ggplot(rtable.box, aes(geno, accuracy.trio)) + geom_boxplot(aes(colour=geno)) + theme_bw() + theme(
    plot.background = element_blank()
   #,panel.grid.major = element_blank()
   #,panel.grid.minor = element_blank()
   #,panel.border = element_blank()
  ) + #+ ylim(0.8,1) #+ xlim(0, 0.6) 
facet_grid( ~ af.labels) + xlab("genotype") + ylab("Accuracy (child/trio)") + ggtitle("Boxplot of Child Accuracy by CN genotype")

```

  
\newpage
#####Comparison of Child Accuracy by CN Genotype?

```{r plots 1b, echo=FALSE, warning=FALSE, fig.align='center'}

rtable.cng5 <- rtable.expand %>%
  filter(size.labels=="N50") %>% 
  filter(geno=="cn2" | geno=="cn1" | geno=="cn0") %>%
  filter(rowname=="cn2" | rowname=="cn1" | rowname=="cn0") %>%
  filter(af.labels=="p=0.5")
rtable.cng3 <- rtable.expand %>%
  filter(size.labels=="N50") %>% 
  filter(geno=="cn2" | geno=="cn1" | geno=="cn0") %>%
  filter(rowname=="cn2" | rowname=="cn1" | rowname=="cn0") %>%
  filter(af.labels=="p=0.3")
rtable.cng1 <- rtable.expand %>%
  filter(size.labels=="N50") %>% 
  filter(geno=="cn2" | geno=="cn1" | geno=="cn0") %>%
  filter(rowname=="cn2" | rowname=="cn1" | rowname=="cn0") %>%
  filter(af.labels=="p=0.1")

ggplot(rtable.cng5, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.5)")

ggplot(rtable.cng3, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.3)")

ggplot(rtable.cng1, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.1)")


```
  
  
\newpage  
#####Comparison of Child Accuracy by CN Genotype and Parental Correctness?

```{r plots 1c, echo=FALSE, warning=FALSE, fig.align='center'}

rtable.cng5pc <- rtable.expand %>%
  filter(size.labels=="N50") %>%
  filter(rowname=="parents.correct.cn2" | rowname=="parents.correct.cn1"| rowname=="parents.correct.cn0") %>%
  filter(af.labels=="p=0.5")
rtable.cng3pc <- rtable.expand %>%
  filter(size.labels=="N50") %>%
  filter(rowname=="parents.correct.cn2" | rowname=="parents.correct.cn1"| rowname=="parents.correct.cn0") %>%
  filter(af.labels=="p=0.3")
rtable.cng1pc <- rtable.expand %>%
  filter(size.labels=="N50") %>%
  filter(rowname=="parents.correct.cn2" | rowname=="parents.correct.cn1"| rowname=="parents.correct.cn0") %>%
  filter(af.labels=="p=0.1")

ggplot(rtable.cng5pc, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.5, parents correct)")

ggplot(rtable.cng3pc, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.3, parents correct)")

ggplot(rtable.cng1pc, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.1, parents correct)")

```
  

```{r plots 1d, echo=FALSE, warning=FALSE, fig.align='center'}
rtable.cng5pic <- rtable.expand %>%
  filter(size.labels=="N50") %>%
  filter(rowname=="parents.incorrect.cn2" | rowname=="parents.incorrect.cn1"| rowname=="parents.incorrect.cn0") %>%
  filter(af.labels=="p=0.5")
rtable.cng3pic <- rtable.expand  %>%
  filter(size.labels=="N50") %>%
  filter(rowname=="parents.incorrect.cn2" | rowname=="parents.incorrect.cn1"| rowname=="parents.incorrect.cn0") %>%
  filter(af.labels=="p=0.3")
rtable.cng1pic <- rtable.expand %>%
  filter(size.labels=="N50") %>%
  filter(rowname=="parents.incorrect.cn2" | rowname=="parents.incorrect.cn1"| rowname=="parents.incorrect.cn0") %>%
  filter(af.labels=="p=0.1")

ggplot(rtable.cng5pic, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.5, parents incorrect)")

ggplot(rtable.cng3pic, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.3, parents incorrect)")

ggplot(rtable.cng1pic, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.1, parents incorrect)")

```
  

```{r plot 1e, echo=F, warning=FALSE, fig.width=9, fig.height=6, fig.align="center"}
rtable.sg <- rtable_sg(rtable.expand)
rtable.sg$sgeno <- str_sub(rtable.sg$rowname,1, 7)

rtable.sg5 <- rtable.sg %>%
  filter(size.labels=="N50") %>%
  filter(af.labels=="p=0.5")

rtable.sg3 <- rtable.sg %>%
  filter(size.labels=="N50") %>%
  filter(af.labels=="p=0.5")

rtable.sg1 <- rtable.sg %>%
  filter(size.labels=="N50") %>%
  filter(af.labels=="p=0.5")

ggplot(rtable.sg5, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Trio Accuracy (Child)") + xlab("Independent Accuracy (Child)") + ggtitle("Child Accuracy by specific parental genotype for p=0.5") + facet_wrap(~sgeno)

ggplot(rtable.sg3, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Trio Accuracy (Child)") + xlab("Independent Accuracy (Child)") + ggtitle("Child Accuracy by specific parental genotype for p=0.3") + facet_wrap(~sgeno)

ggplot(rtable.sg1, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Trio Accuracy (Child)") + xlab("Independent Accuracy (Child)") + ggtitle("Child Accuracy by specific parental genotype for p=0.1") + facet_wrap(~sgeno)

```
  

\newpage
#### N=100

```{r n2, echo=FALSE}
file.no1 <- seq(2,leng, by=12)
file.no2 <- seq(6,leng, by=12)
file.no3 <- seq(10,leng, by=12)
file.no <- sort(c(file.no1, file.no2, file.no3))

results.list1 <- results.list[file.no]
results.list1a <- results.list[file.no1]
results.list1b <- results.list[file.no2]
results.list1c <- results.list[file.no3]

rtable1 <- output_results2(results.list1)
rtable1a <- output_results2(results.list1a)
rtable1b <- output_results2(results.list1b)
rtable1c <- output_results2(results.list1c)
```


#####What is the overall accuracy for N=100?

```{r data2a, echo=F}

rtable.overall <- rtable_overall(rtable1)
#rtable.osmaller <- rtable_overalls(rtable1)
kable(rtable.overall) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```

#####What is the overall accuracy for N=100 by allele frequency?

```{r data2b, echo=F}

#rtable.af <- rtable_af(rtable1a, rtable1b, rtable1c)
rtable.afs <- rtable_afs(rtable1a, rtable1b, rtable1c)
kable(rtable.afs) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```
  
  
\newpage
#####What is the accuracy for N=100 by allele frequency stratified by whether parents were genotyped correctly?


```{r data2c, echo=F}

#rtable.pc <- rtable_pc(rtable1a, rtable1b, rtable1c)
rtable.pcs <- rtable_pcs(rtable1a, rtable1b, rtable1c)
kable(rtable.pcs, caption = "Parents Correct") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

#rtable.pic <- rtable_pic(rtable1a, rtable1b, rtable1c)
rtable.pics <- rtable_pics(rtable1a, rtable1b, rtable1c)
kable(rtable.pics, caption = "Parents Incorrect") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```
  
  
\newpage
#####What is the accuracy for N=100 by specific parental genotype?


```{r data2d, echo=F}

rtable.geno1 <- rtable_geno(rtable1a)
rtable.geno2 <- rtable_geno(rtable1b)
rtable.geno3 <- rtable_geno(rtable1c)

kable(rtable.geno1, caption = "p=0.5") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
kable(rtable.geno2, caption = "p=0.3") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
kable(rtable.geno3, caption = "p=0.1") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```

\newpage  
#####Comparison of Overall Child Accuracy?


```{r comparison 2, echo=FALSE, warning=FALSE}

rtable.accur <- rtable.expand %>% 
  filter(geno=="all") %>%
  filter(size.labels=="N100")
ggplot(rtable.accur, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=af.labels)) + geom_abline(intercept=0) + xlim(0.5,1) + ylim(0.5,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Overall Child Accuracy")
```
  
  
\newpage
#####What does the data look like across the replicates (boxplot)?

```{r plots 2a, echo=FALSE, warning=FALSE, fig.align='center'}
rtable.box <- rtable.expand %>%
  filter(geno=="cn2" | geno=="cn1" | geno=="cn0") %>%
  filter(size.labels=="N100")
ggplot(rtable.box, aes(geno, accuracy.trio)) + geom_boxplot(aes(colour=geno)) + theme_bw() + theme(
    plot.background = element_blank()
   #,panel.grid.major = element_blank()
   #,panel.grid.minor = element_blank()
   #,panel.border = element_blank()
  ) + #+ ylim(0.8,1) #+ xlim(0, 0.6) 
facet_grid( ~ af.labels) + xlab("genotype") + ylab("Accuracy (child/trio)") + ggtitle("Boxplot of Child Accuracy by CN genotype")

```

  
\newpage
#####Comparison of Child Accuracy by CN Genotype?

```{r plots 2b, echo=FALSE, warning=FALSE, fig.align='center'}

rtable.cng5 <- rtable.expand %>%
  filter(size.labels=="N100") %>% 
  filter(geno=="cn2" | geno=="cn1" | geno=="cn0") %>%
  filter(rowname=="cn2" | rowname=="cn1" | rowname=="cn0") %>%
  filter(af.labels=="p=0.5")
rtable.cng3 <- rtable.expand %>%
  filter(size.labels=="N100") %>% 
  filter(geno=="cn2" | geno=="cn1" | geno=="cn0") %>%
  filter(rowname=="cn2" | rowname=="cn1" | rowname=="cn0") %>%
  filter(af.labels=="p=0.3")
rtable.cng1 <- rtable.expand %>%
  filter(size.labels=="N100") %>% 
  filter(geno=="cn2" | geno=="cn1" | geno=="cn0") %>%
  filter(rowname=="cn2" | rowname=="cn1" | rowname=="cn0") %>%
  filter(af.labels=="p=0.1")

ggplot(rtable.cng5, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.5)")

ggplot(rtable.cng3, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.3)")

ggplot(rtable.cng1, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.1)")


```
  
  
\newpage  
#####Comparison of Child Accuracy by CN Genotype and Parental Correctness?

```{r plots 2c, echo=FALSE, warning=FALSE, fig.align='center'}

rtable.cng5pc <- rtable.expand %>%
  filter(size.labels=="N100") %>%
  filter(rowname=="parents.correct.cn2" | rowname=="parents.correct.cn1"| rowname=="parents.correct.cn0") %>%
  filter(af.labels=="p=0.5")
rtable.cng3pc <- rtable.expand %>%
  filter(size.labels=="N100") %>%
  filter(rowname=="parents.correct.cn2" | rowname=="parents.correct.cn1"| rowname=="parents.correct.cn0") %>%
  filter(af.labels=="p=0.3")
rtable.cng1pc <- rtable.expand %>%
  filter(size.labels=="N100") %>%
  filter(rowname=="parents.correct.cn2" | rowname=="parents.correct.cn1"| rowname=="parents.correct.cn0") %>%
  filter(af.labels=="p=0.1")

ggplot(rtable.cng5pc, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.5, parents correct)")

ggplot(rtable.cng3pc, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.3, parents correct)")

ggplot(rtable.cng1pc, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.1, parents correct)")

```
  

```{r plots 2d, echo=FALSE, warning=FALSE, fig.align='center'}
rtable.cng5pic <- rtable.expand %>%
  filter(size.labels=="N100") %>%
  filter(rowname=="parents.incorrect.cn2" | rowname=="parents.incorrect.cn1"| rowname=="parents.incorrect.cn0") %>%
  filter(af.labels=="p=0.5")
rtable.cng3pic <- rtable.expand  %>%
  filter(size.labels=="N100") %>%
  filter(rowname=="parents.incorrect.cn2" | rowname=="parents.incorrect.cn1"| rowname=="parents.incorrect.cn0") %>%
  filter(af.labels=="p=0.3")
rtable.cng1pic <- rtable.expand %>%
  filter(size.labels=="N100") %>%
  filter(rowname=="parents.incorrect.cn2" | rowname=="parents.incorrect.cn1"| rowname=="parents.incorrect.cn0") %>%
  filter(af.labels=="p=0.1")

ggplot(rtable.cng5pic, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.5, parents incorrect)")

ggplot(rtable.cng3pic, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.3, parents incorrect)")

ggplot(rtable.cng1pic, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.1, parents incorrect)")

```
  

```{r plot 2e, echo=F, warning=FALSE, fig.width=9, fig.height=6, fig.align="center"}
rtable.sg <- rtable_sg(rtable.expand)
rtable.sg$sgeno <- str_sub(rtable.sg$rowname,1, 7)

rtable.sg5 <- rtable.sg %>%
  filter(size.labels=="N100") %>%
  filter(af.labels=="p=0.5")

rtable.sg3 <- rtable.sg %>%
  filter(size.labels=="N100") %>%
  filter(af.labels=="p=0.5")

rtable.sg1 <- rtable.sg %>%
  filter(size.labels=="N100") %>%
  filter(af.labels=="p=0.5")

ggplot(rtable.sg5, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Trio Accuracy (Child)") + xlab("Independent Accuracy (Child)") + ggtitle("Child Accuracy by specific parental genotype for p=0.5") + facet_wrap(~sgeno)

ggplot(rtable.sg3, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Trio Accuracy (Child)") + xlab("Independent Accuracy (Child)") + ggtitle("Child Accuracy by specific parental genotype for p=0.3") + facet_wrap(~sgeno)

ggplot(rtable.sg1, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Trio Accuracy (Child)") + xlab("Independent Accuracy (Child)") + ggtitle("Child Accuracy by specific parental genotype for p=0.1") + facet_wrap(~sgeno)

```
  
\newpage
#### N=250

```{r n3, echo=FALSE}
file.no1 <- seq(3,leng, by=12)
file.no2 <- seq(7,leng, by=12)
file.no3 <- seq(11,leng, by=12)
file.no <- sort(c(file.no1, file.no2, file.no3))

results.list1 <- results.list[file.no]
results.list1a <- results.list[file.no1]
results.list1b <- results.list[file.no2]
results.list1c <- results.list[file.no3]

rtable1 <- output_results2(results.list1)
rtable1a <- output_results2(results.list1a)
rtable1b <- output_results2(results.list1b)
rtable1c <- output_results2(results.list1c)
```


#####What is the overall accuracy for N=250?

```{r data3a, echo=F}

rtable.overall <- rtable_overall(rtable1)
#rtable.osmaller <- rtable_overalls(rtable1)
kable(rtable.overall) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```

#####What is the overall accuracy for N=250 by allele frequency?

```{r data3b, echo=F}

#rtable.af <- rtable_af(rtable1a, rtable1b, rtable1c)
rtable.afs <- rtable_afs(rtable1a, rtable1b, rtable1c)
kable(rtable.afs) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```
  
  
\newpage
#####What is the accuracy for N=250 by allele frequency stratified by whether parents were genotyped correctly?


```{r data3c, echo=F}

#rtable.pc <- rtable_pc(rtable1a, rtable1b, rtable1c)
rtable.pcs <- rtable_pcs(rtable1a, rtable1b, rtable1c)
kable(rtable.pcs, caption = "Parents Correct") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

#rtable.pic <- rtable_pic(rtable1a, rtable1b, rtable1c)
rtable.pics <- rtable_pics(rtable1a, rtable1b, rtable1c)
kable(rtable.pics, caption = "Parents Incorrect") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```
  
  
\newpage
#####What is the accuracy for N=250 by specific parental genotype?


```{r data3d, echo=F}

rtable.geno1 <- rtable_geno(rtable1a)
rtable.geno2 <- rtable_geno(rtable1b)
rtable.geno3 <- rtable_geno(rtable1c)

kable(rtable.geno1, caption = "p=0.5") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
kable(rtable.geno2, caption = "p=0.3") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
kable(rtable.geno3, caption = "p=0.1") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```

\newpage  
#####Comparison of Overall Child Accuracy?


```{r comparison 3, echo=FALSE, warning=FALSE}

rtable.accur <- rtable.expand %>% 
  filter(geno=="all") %>%
  filter(size.labels=="N250")
ggplot(rtable.accur, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=af.labels)) + geom_abline(intercept=0) + xlim(0.5,1) + ylim(0.5,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Overall Child Accuracy")
```
  
  
\newpage
#####What does the data look like across the replicates (boxplot)?

```{r plots 3a, echo=FALSE, warning=FALSE, fig.align='center'}
rtable.box <- rtable.expand %>%
  filter(geno=="cn2" | geno=="cn1" | geno=="cn0") %>%
  filter(size.labels=="N250")
ggplot(rtable.box, aes(geno, accuracy.trio)) + geom_boxplot(aes(colour=geno)) + theme_bw() + theme(
    plot.background = element_blank()
   #,panel.grid.major = element_blank()
   #,panel.grid.minor = element_blank()
   #,panel.border = element_blank()
  ) + #+ ylim(0.8,1) #+ xlim(0, 0.6) 
facet_grid( ~ af.labels) + xlab("genotype") + ylab("Accuracy (child/trio)") + ggtitle("Boxplot of Child Accuracy by CN genotype")

```

  
\newpage
#####Comparison of Child Accuracy by CN Genotype?

```{r plots 3b, echo=FALSE, warning=FALSE, fig.align='center'}

rtable.cng5 <- rtable.expand %>%
  filter(size.labels=="N250") %>% 
  filter(geno=="cn2" | geno=="cn1" | geno=="cn0") %>%
  filter(rowname=="cn2" | rowname=="cn1" | rowname=="cn0") %>%
  filter(af.labels=="p=0.5")
rtable.cng3 <- rtable.expand %>%
  filter(size.labels=="N250") %>% 
  filter(geno=="cn2" | geno=="cn1" | geno=="cn0") %>%
  filter(rowname=="cn2" | rowname=="cn1" | rowname=="cn0") %>%
  filter(af.labels=="p=0.3")
rtable.cng1 <- rtable.expand %>%
  filter(size.labels=="N250") %>% 
  filter(geno=="cn2" | geno=="cn1" | geno=="cn0") %>%
  filter(rowname=="cn2" | rowname=="cn1" | rowname=="cn0") %>%
  filter(af.labels=="p=0.1")

ggplot(rtable.cng5, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.5)")

ggplot(rtable.cng3, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.3)")

ggplot(rtable.cng1, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.1)")


```
  
  
\newpage  
#####Comparison of Child Accuracy by CN Genotype and Parental Correctness?

```{r plots 3c, echo=FALSE, warning=FALSE, fig.align='center'}

rtable.cng5pc <- rtable.expand %>%
  filter(size.labels=="N250") %>%
  filter(rowname=="parents.correct.cn2" | rowname=="parents.correct.cn1"| rowname=="parents.correct.cn0") %>%
  filter(af.labels=="p=0.5")
rtable.cng3pc <- rtable.expand %>%
  filter(size.labels=="N250") %>%
  filter(rowname=="parents.correct.cn2" | rowname=="parents.correct.cn1"| rowname=="parents.correct.cn0") %>%
  filter(af.labels=="p=0.3")
rtable.cng1pc <- rtable.expand %>%
  filter(size.labels=="N250") %>%
  filter(rowname=="parents.correct.cn2" | rowname=="parents.correct.cn1"| rowname=="parents.correct.cn0") %>%
  filter(af.labels=="p=0.1")

ggplot(rtable.cng5pc, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.5, parents correct)")

ggplot(rtable.cng3pc, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.3, parents correct)")

ggplot(rtable.cng1pc, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.1, parents correct)")

```
  

```{r plots 3d, echo=FALSE, warning=FALSE, fig.align='center'}
rtable.cng5pic <- rtable.expand %>%
  filter(size.labels=="N250") %>%
  filter(rowname=="parents.incorrect.cn2" | rowname=="parents.incorrect.cn1"| rowname=="parents.incorrect.cn0") %>%
  filter(af.labels=="p=0.5")
rtable.cng3pic <- rtable.expand  %>%
  filter(size.labels=="N250") %>%
  filter(rowname=="parents.incorrect.cn2" | rowname=="parents.incorrect.cn1"| rowname=="parents.incorrect.cn0") %>%
  filter(af.labels=="p=0.3")
rtable.cng1pic <- rtable.expand %>%
  filter(size.labels=="N250") %>%
  filter(rowname=="parents.incorrect.cn2" | rowname=="parents.incorrect.cn1"| rowname=="parents.incorrect.cn0") %>%
  filter(af.labels=="p=0.1")

ggplot(rtable.cng5pic, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.5, parents incorrect)")

ggplot(rtable.cng3pic, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.3, parents incorrect)")

ggplot(rtable.cng1pic, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.1, parents incorrect)")

```
  

```{r plot 3e, echo=F, warning=FALSE, fig.width=9, fig.height=6, fig.align="center"}
rtable.sg <- rtable_sg(rtable.expand)
rtable.sg$sgeno <- str_sub(rtable.sg$rowname,1, 7)

rtable.sg5 <- rtable.sg %>%
  filter(size.labels=="N250") %>%
  filter(af.labels=="p=0.5")

rtable.sg3 <- rtable.sg %>%
  filter(size.labels=="N250") %>%
  filter(af.labels=="p=0.5")

rtable.sg1 <- rtable.sg %>%
  filter(size.labels=="N250") %>%
  filter(af.labels=="p=0.5")

ggplot(rtable.sg5, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Trio Accuracy (Child)") + xlab("Independent Accuracy (Child)") + ggtitle("Child Accuracy by specific parental genotype for p=0.5") + facet_wrap(~sgeno)

ggplot(rtable.sg3, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Trio Accuracy (Child)") + xlab("Independent Accuracy (Child)") + ggtitle("Child Accuracy by specific parental genotype for p=0.3") + facet_wrap(~sgeno)

ggplot(rtable.sg1, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Trio Accuracy (Child)") + xlab("Independent Accuracy (Child)") + ggtitle("Child Accuracy by specific parental genotype for p=0.1") + facet_wrap(~sgeno)

```
  
\newpage
#### N=1000

```{r n4, echo=FALSE}
# for p=0.5
file.no1 <- seq(4,leng, by=12)

# for p=0.3
file.no2 <- seq(8,leng, by=12)

# for p=0.1
file.no3 <- seq(12,leng, by=12)
file.no <- sort(c(file.no1, file.no2, file.no3))
results.list1 <- results.list[file.no]
results.list1a <- results.list[file.no1]
results.list1b <- results.list[file.no2]
results.list1c <- results.list[file.no3]

rtable1 <- output_results2(results.list1)
rtable1a <- output_results2(results.list1a)
rtable1b <- output_results2(results.list1b)
rtable1c <- output_results2(results.list1c)
```


#####What is the overall accuracy for N=1000?

```{r data4a, echo=F}

rtable.overall <- rtable_overall(rtable1)
#rtable.osmaller <- rtable_overalls(rtable1)
kable(rtable.overall) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```

#####What is the overall accuracy for N=1000 by allele frequency?

```{r data4b, echo=F}

#rtable.af <- rtable_af(rtable1a, rtable1b, rtable1c)
rtable.afs <- rtable_afs(rtable1a, rtable1b, rtable1c)
kable(rtable.afs) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```
  
  
\newpage
#####What is the accuracy for N=1000 by allele frequency stratified by whether parents were genotyped correctly?


```{r data4c, echo=F}

#rtable.pc <- rtable_pc(rtable1a, rtable1b, rtable1c)
rtable.pcs <- rtable_pcs(rtable1a, rtable1b, rtable1c)
kable(rtable.pcs, caption = "Parents Correct") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

#rtable.pic <- rtable_pic(rtable1a, rtable1b, rtable1c)
rtable.pics <- rtable_pics(rtable1a, rtable1b, rtable1c)
kable(rtable.pics, caption = "Parents Incorrect") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```
  
  
\newpage
#####What is the accuracy for N=1000 by specific parental genotype?


```{r data4d, echo=F}

rtable.geno1 <- rtable_geno(rtable1a)
rtable.geno2 <- rtable_geno(rtable1b)
rtable.geno3 <- rtable_geno(rtable1c)

kable(rtable.geno1, caption = "p=0.5") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
kable(rtable.geno2, caption = "p=0.3") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
kable(rtable.geno3, caption = "p=0.1") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))

```

\newpage  
#####Comparison of Overall Child Accuracy?


```{r comparison 4, echo=FALSE, warning=FALSE}

rtable.accur <- rtable.expand %>% 
  filter(geno=="all") %>%
  filter(size.labels=="N1000")
ggplot(rtable.accur, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=af.labels)) + geom_abline(intercept=0) + xlim(0.5,1) + ylim(0.5,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Overall Child Accuracy")
```
  
  
\newpage
#####What does the data look like across the replicates (boxplot)?

```{r plots 4a, echo=FALSE, warning=FALSE, fig.align='center'}
rtable.box <- rtable.expand %>%
  filter(geno=="cn2" | geno=="cn1" | geno=="cn0") %>%
  filter(size.labels=="N1000")
ggplot(rtable.box, aes(geno, accuracy.trio)) + geom_boxplot(aes(colour=geno)) + theme_bw() + theme(
    plot.background = element_blank()
   #,panel.grid.major = element_blank()
   #,panel.grid.minor = element_blank()
   #,panel.border = element_blank()
  ) + #+ ylim(0.8,1) #+ xlim(0, 0.6) 
facet_grid( ~ af.labels) + xlab("genotype") + ylab("Accuracy (child/trio)") + ggtitle("Boxplot of Child Accuracy by CN genotype")

```

  
\newpage
#####Comparison of Child Accuracy by CN Genotype?

```{r plots 4b, echo=FALSE, warning=FALSE, fig.align='center'}

rtable.cng5 <- rtable.expand %>%
  filter(size.labels=="N1000") %>% 
  filter(geno=="cn2" | geno=="cn1" | geno=="cn0") %>%
  filter(rowname=="cn2" | rowname=="cn1" | rowname=="cn0") %>%
  filter(af.labels=="p=0.5")
rtable.cng3 <- rtable.expand %>%
  filter(size.labels=="N1000") %>% 
  filter(geno=="cn2" | geno=="cn1" | geno=="cn0") %>%
  filter(rowname=="cn2" | rowname=="cn1" | rowname=="cn0") %>%
  filter(af.labels=="p=0.3")
rtable.cng1 <- rtable.expand %>%
  filter(size.labels=="N1000") %>% 
  filter(geno=="cn2" | geno=="cn1" | geno=="cn0") %>%
  filter(rowname=="cn2" | rowname=="cn1" | rowname=="cn0") %>%
  filter(af.labels=="p=0.1")

ggplot(rtable.cng5, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.5)")

ggplot(rtable.cng3, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.3)")

ggplot(rtable.cng1, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.1)")


```
  
  
\newpage  
#####Comparison of Child Accuracy by CN Genotype and Parental Correctness?

```{r plots 4c, echo=FALSE, warning=FALSE, fig.align='center'}

rtable.cng5pc <- rtable.expand %>%
  filter(size.labels=="N1000") %>%
  filter(rowname=="parents.correct.cn2" | rowname=="parents.correct.cn1"| rowname=="parents.correct.cn0") %>%
  filter(af.labels=="p=0.5")
rtable.cng3pc <- rtable.expand %>%
  filter(size.labels=="N1000") %>%
  filter(rowname=="parents.correct.cn2" | rowname=="parents.correct.cn1"| rowname=="parents.correct.cn0") %>%
  filter(af.labels=="p=0.3")
rtable.cng1pc <- rtable.expand %>%
  filter(size.labels=="N1000") %>%
  filter(rowname=="parents.correct.cn2" | rowname=="parents.correct.cn1"| rowname=="parents.correct.cn0") %>%
  filter(af.labels=="p=0.1")

ggplot(rtable.cng5pc, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.5, parents correct)")

ggplot(rtable.cng3pc, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.3, parents correct)")

ggplot(rtable.cng1pc, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.1, parents correct)")

```
  

```{r plots 4d, echo=FALSE, warning=FALSE, fig.align='center'}
rtable.cng5pic <- rtable.expand %>%
  filter(size.labels=="N1000") %>%
  filter(rowname=="parents.incorrect.cn2" | rowname=="parents.incorrect.cn1"| rowname=="parents.incorrect.cn0") %>%
  filter(af.labels=="p=0.5")
rtable.cng3pic <- rtable.expand  %>%
  filter(size.labels=="N1000") %>%
  filter(rowname=="parents.incorrect.cn2" | rowname=="parents.incorrect.cn1"| rowname=="parents.incorrect.cn0") %>%
  filter(af.labels=="p=0.3")
rtable.cng1pic <- rtable.expand %>%
  filter(size.labels=="N1000") %>%
  filter(rowname=="parents.incorrect.cn2" | rowname=="parents.incorrect.cn1"| rowname=="parents.incorrect.cn0") %>%
  filter(af.labels=="p=0.1")

ggplot(rtable.cng5pic, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.5, parents incorrect)")

ggplot(rtable.cng3pic, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.3, parents incorrect)")

ggplot(rtable.cng1pic, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Child Accuracy") + xlab("Independent Accuracy") + ggtitle("Child Accuracy by Genotype (p=0.1, parents incorrect)")

```
  

```{r plot 4e, echo=F, warning=FALSE, fig.width=9, fig.height=6, fig.align="center"}
rtable.sg <- rtable_sg(rtable.expand)
rtable.sg$sgeno <- str_sub(rtable.sg$rowname,1, 7)

rtable.sg5 <- rtable.sg %>%
  filter(size.labels=="N1000") %>%
  filter(af.labels=="p=0.5")

rtable.sg3 <- rtable.sg %>%
  filter(size.labels=="N1000") %>%
  filter(af.labels=="p=0.5")

rtable.sg1 <- rtable.sg %>%
  filter(size.labels=="N1000") %>%
  filter(af.labels=="p=0.5")

ggplot(rtable.sg5, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Trio Accuracy (Child)") + xlab("Independent Accuracy (Child)") + ggtitle("Child Accuracy by specific parental genotype for p=0.5") + facet_wrap(~sgeno)

ggplot(rtable.sg3, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Trio Accuracy (Child)") + xlab("Independent Accuracy (Child)") + ggtitle("Child Accuracy by specific parental genotype for p=0.3") + facet_wrap(~sgeno)

ggplot(rtable.sg1, aes(accuracy.ind, accuracy.trio)) + geom_jitter(aes(colour=geno)) + geom_abline(intercept=0) + xlim(0,1) + ylim(0,1) + ylab("Trio Accuracy (Child)") + xlab("Independent Accuracy (Child)") + ggtitle("Child Accuracy by specific parental genotype for p=0.1") + facet_wrap(~sgeno)

```
  